\documentclass{sig-alternate-05-2015}
\include{macros}

\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
%\doi{10.475/123_4}

% ISBN
%\isbn{123-4567-24-567/08/06}

%Conference
\conferenceinfo{MSR '16}{May 14--15, 2016, Austin, TX, USA}

%\acmPrice{\$15.00}

%
% --- Author Metadata here ---
\conferenceinfo{MSR}{'16 Austin, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

%
% General information
%
\title{\mytitle}

\numberofauthors{6}

\author{
    \alignauthor
    Carlos Gómez Teshima\\
    \affaddr{University of Victoria}\\
    \affaddr{Victoria, BC, Canada}\\
    \email{teshima@uvic.ca}
    \alignauthor 
    Daniel M. German\\
    \affaddr{University of Victoria}\\
    \affaddr{Victoria, BC, Canada}\\
    \email{dmg@uvic.ca}
    \alignauthor
    Alexey Zagalsky\\
    \affaddr{University of Victoria}\\
    \affaddr{Victoria, BC, Canada}\\
    \email{alexeyza@uvic.ca}
    \and
    \alignauthor
    Margaret-Anne Storey\\
    \affaddr{University of Victoria}\\
    \affaddr{Victoria, BC, Canada}\\
    \email{mstorey@uvic.ca}
    \alignauthor 
    Germán Poo-Caamaño\\
    \affaddr{University of Victoria}\\
    \affaddr{Victoria, BC, Canada}\\
    \email{gpoo@uvic.ca}
}

\date{\the\year}

\maketitle

\begin{abstract}
	Media channels play an important role in the flow, construction, and curation of knowledge in software development.
	Understanding how developers use media channels is key to improving developer practices and supporting channel evolution.
	In this paper, we report the way developers use media channels to curate knowledge within the R software development community.
	By applying a case study methodology consisting of mining archival data and survey methods, we investigated the R community on Stack Overflow and the R-help mailing list, using a qualitative approach.
	The findings reveal that Stack Overflow and mailing lists foster knowledge co-construction differently---crowd-sourced and participatory, respectively.
	Furthermore, developers use actively both channels to optimize knowledge exchange and curation.

	This paper contributes to the understanding of knowledge curation by developer communities, and describes a model for a systematic comparison of two or more media channels within a community of practice.
	The model enables knowledge categorization and further studies to explore knowledge flow within multiple media channels.
	Based on our observations and a survey data analysis, we extracted a set of recommendations to assist practitioners in the use of multiple Question and Answer (Q\&A) channels.
\end{abstract}

%
% The code below was generated with the tool at
% http://dl.acm.org/ccs.cfm
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003120.10003130.10003131.10003235</concept_id>
<concept_desc>Human-centered computing~Collaborative content creation</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Human-centered computing~Collaborative content creation}

%
% End generated code
%

%
%  Use this command to print the description
%
\printccsdesc

\keywords{\mykeywords}

\input{1-introduction.tex}
\input{2-background.tex}
\input{3-methodology.tex}
\input{4-findings.tex}
\input{5-discussion.tex}
\input{6-conclusions.tex}

\bibliographystyle{abbrv}
\bibliography{references}

\end{document}
